---
title: "Binomial and Normal Distribution Convergence"
output: html_document
date: "2024-06-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Convergence of Binomial and Normal Distributions

#Motivation
In probability theory, the normal distribution may be used as an approximation to the binomial distribution under certain conditions. Specifically, as the number of trials "N" becomes large, the binomial distribution with parameters "N" and "p" converges to a normal distribution with mean mu = Np and variance sigma^2 = Np(1-p).

##Load Packages
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

##Set seed for reproducibility
```{r}
set.seed(123)
```

##Parameters for binomial distribution
```{r}
n<- 1000
p<- 0.5
```

##Generate data for binomial distribution with large N
```{r}
binom_dat<- rbinom(1000, size=n , prob = p)
binom_df<- data.frame(value=binom_dat)
```

##Generate data for normal distribution
```{r}
mean<- n*p
sd<- sqrt(n*p*(1-p))
norm_dat <- rnorm(1000, mean=mean, sd=sd)
norm_df <- data.frame(value=norm_dat)

```

##Binomial histogram
```{r}
binom_plot<- ggplot(binom_df, aes(x=value))+geom_histogram(binwidth=30, fill="blue", color="black", alpha =0.7)+labs(title="Binomial Distribution", x="Value", y="Frequency")+theme_minimal()
```

##Normal histogram
```{r}
norm_plot<- ggplot(norm_df, aes(x=value))+geom_histogram(binwidth = 30, fill="red", color="black", alpha=0.7) +labs("Normal Distribution", x="Value", y="Frequency")+theme_minimal()
```

##Produce plots
```{r}
ggsave("binom_plot.png", binom_plot)
ggsave("norm_plot.png", norm_plot)
plot(binom_plot)
plot(norm_plot)
```

#Conclusion
The histograms display the binomial distribution with a large number of trials N and probability p converges to a normal distribution with the same mean and variance. This visualization aligns with the theoretical convergence described by the central limit theorem.
